The evolution of gene expression in the term placenta of viviparous mammals

### 2015-12-18 manuscript/manuscript.Rnw
include tmbs1 tree

>>>>

\begin{figure}
<<tmsb1.receptor.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="TMSB10" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression)
@ 
\caption{Expression of \textit{TMSB1}}
\label{fig:tmsb1_evolution_tree}
\end{figure}
